Raw Traces

### 2023-05-22 Fish Data Analysis/Raw Traces Figure.qmd
Reverting to old files, fixing 3d matching errors

>>>>

### Final Version Dark
No flow

nnd_frame <- 130

example_data <- comp_data_all %>% filter(Data_ID == "2021_10_8_15")

smooth_data <- example_data %>% group_by(Fish1,Frame_Num) %>%
                               summarise(Fish1_X = mean(Fish1_X),
                                         Fish1_Y = mean(Fish1_Y),
                                         Fish1_Z = mean(Fish1_Z)) %>%
                               group_by(Fish1) %>%
                               mutate(Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
                                      Fish1_X_Smooth = na.spline(Fish1_X_Smooth) + 0*na.approx(Fish1_X_Smooth, na.rm = FALSE),
                                      Fish1_Y_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Y),
                                      Fish1_Y_Smooth = na.spline(Fish1_Y_Smooth) + 0*na.approx(Fish1_Y_Smooth, na.rm = FALSE),
                                      Fish1_Z_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Z),
                                      Fish1_Z_Smooth = na.spline(Fish1_Z_Smooth) + 0*na.approx(Fish1_Z_Smooth, na.rm = FALSE)) %>%
                               ungroup() #%>% 
                               #filter(Fish1_Z_Smooth >= -0.5 & Fish1_Z_Smooth <= 5)

smooth_data_nnd <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish1_Z,Fish2_X,Fish2_Y,Fish1_Z)) %>%
                                    group_by(Fish1,Frame_Num) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    filter(row_n == 1) %>%
                                    ungroup() %>%
                                    group_by(Fish1) %>%
                                    arrange(Frame_Num) %>%
                                    mutate(Fish1_Distance_Smooth = supsmu_right_length_y(Frame_Num,nndDistance),
                                           Fish1_Distance_Smooth = na.spline(Fish1_Distance_Smooth) + 0*na.approx(Fish1_Distance_Smooth, na.rm = FALSE)) %>%
                                    ungroup() #%>% 
                                    #filter(Fish1_Z >= -2 & Fish1_Z <= 5)

select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
                                          filter(Frame_Num %in% c(0, 240, nnd_frame)) %>% 
                                          left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
                                          group_by(Fish1, Frame_Num) %>%
                                          summarise(Fish1_X_Smooth = mean(Fish1_X_Smooth),
                                                    Fish1_Y_Smooth = mean(Fish1_Y_Smooth),
                                                    Fish1_Z_Smooth = mean(Fish1_Z_Smooth))

nnd_joined <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y)) %>%
                                    group_by(Fish1,Frame_Num) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance <= 2 | all_nas) %>%
                                    mutate(row_n = row_number(),
                                           remove = ifelse(row_n > 1 & is.na(Distance),"Y","N")) %>%
                                    filter(remove == "N") %>%
                                    ungroup() %>%
                                    filter(Frame_Num %in% c(nnd_frame)) %>% 
                                    mutate(Grouping = paste(Frame_Num, Fish1, Fish2)) %>% 
                                    select(c(Frame_Num, Fish1, Fish2, Grouping)) %>%
                                    pivot_longer(c(Fish1, Fish2),
                                                  names_to = "Useless",
                                                  values_to = "Fish1") %>%
                                    select(-c(Useless)) %>% 
                                    left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth))

raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num/60, y = Fish1_Distance_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  geom_line(data = nnd_summary, aes(x = Frame_Num/60, y = meanNND_Smooth), color = "black", size = 1.5)+
  scale_color_manual(values = c("#ea4747","#df4415","#ff7489","#4790ea","#47ea4b", "#15c9df", "#8574ff", "#09b326"))+
  theme_classic()+ 
  theme(legend.position = "none")+
  xlab("Time (s)")+
  ylab("NND (BL)")+
  ylim(0,3)

raw_nnd_plot

axis_remove <- list(showaxeslabels  = FALSE,
                    showgrid = FALSE,
                    showline = FALSE,
                    showticklabels = FALSE,
                    showspikes = FALSE,
                    showticklabels  = FALSE,
                    visible = FALSE,
                    zeroline = FALSE)

fig <- plot_ly() %>%
        #groups and colors
        # 1, 2, 3: ea4747, df1574, fdbe6f
        # 5, 8: 32CD32, 006400
        # 4, 6, 7: 4790ea, 8115df, 45dfef
        # Old: c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")
        # New: c("#ea4747","#df1574","#fdbe6f","#4790ea","#32CD32", "#8115df", "#45dfef", "#006400")

       add_trace(x = smooth_data$Fish1_X_Smooth, y = smooth_data$Fish1_Y_Smooth, z = smooth_data$Fish1_Z_Smooth,
               split = smooth_data$Fish1, type = 'scatter3d', mode = 'lines', opacity = 1, line = list(width = 6),
               color = smooth_data$Fish1,
               colors = c("#ea4747","#df1574","#fdbe6f","#4790ea","#32CD32", "#8115df", "#45dfef", "#006400")) %>%

       add_trace(x = select_frames_labeled$Fish1_X_Smooth, y = select_frames_labeled$Fish1_Y_Smooth, z = select_frames_labeled$Fish1_Z_Smooth,
                 split = select_frames_labeled$Fish1, type = 'scatter3d', mode = "markers",
                 color = select_frames_labeled$Fish1,
                 colors = c("#ea4747","#df1574","#fdbe6f","#4790ea","#32CD32", "#8115df", "#45dfef", "#006400")) %>%

       add_trace(x = nnd_joined$Fish1_X_Smooth, y = nnd_joined$Fish1_Y_Smooth, z = nnd_joined$Fish1_Z_Smooth, 
                 split = nnd_joined$Grouping, type = 'scatter3d', mode = "lines", color = I("black"), line = list(shape = "spline", width = 10)) %>%

       layout(showlegend = FALSE, scene = list(aspectratio=list(x=2,y=1,z=1),
              xaxis = axis_remove, 
              yaxis = axis_remove,
              zaxis = axis_remove))

## Non Darkness Figure

unique((comp_data_all %>% filter(Darkness == "Light" & Flow == "Still Water"))$Data_ID)

### Final Version

#2021_8_3_7 !
#2021_10_6_38 Not as good

nnd_frame <- 120

example_data <- comp_data_all %>% filter(Data_ID == "2021_8_3_7")

smooth_data <- example_data %>% group_by(Fish1,Frame_Num) %>%
                               summarise(Fish1_X = mean(Fish1_X),
                                         Fish1_Y = mean(Fish1_Y),
                                         Fish1_Z = mean(Fish1_Z)) %>%
                               group_by(Fish1) %>%
                               mutate(Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
                                      Fish1_X_Smooth = na.spline(Fish1_X_Smooth) + 0*na.approx(Fish1_X_Smooth, na.rm = FALSE),
                                      Fish1_Y_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Y),
                                      Fish1_Y_Smooth = na.spline(Fish1_Y_Smooth) + 0*na.approx(Fish1_Y_Smooth, na.rm = FALSE),
                                      Fish1_Z_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Z),
                                      Fish1_Z_Smooth = na.spline(Fish1_Z_Smooth) + 0*na.approx(Fish1_Z_Smooth, na.rm = FALSE)) %>%
                               ungroup() #%>% 
                               #filter(Fish1_Z_Smooth >= -0.5 & Fish1_Z_Smooth <= 5)

smooth_data_nnd <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish1_Z,Fish2_X,Fish2_Y,Fish1_Z)) %>%
                                    group_by(Fish1,Frame_Num) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    filter(row_n == 1) %>%
                                    ungroup() %>%
                                    group_by(Fish1) %>%
                                    arrange(Frame_Num) %>%
                                    mutate(Fish1_Distance_Smooth = supsmu_right_length_y(Frame_Num,nndDistance),
                                           Fish1_Distance_Smooth = na.spline(Fish1_Distance_Smooth) + 0*na.approx(Fish1_Distance_Smooth, na.rm = FALSE)) %>%
                                    ungroup() #%>% 
                                    #filter(Fish1_Z >= -2 & Fish1_Z <= 5)

select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
                                          filter(Frame_Num %in% c(0, 240, nnd_frame)) %>% 
                                          left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
                                          group_by(Fish1, Frame_Num) %>%
                                          summarise(Fish1_X_Smooth = mean(Fish1_X_Smooth),
                                                    Fish1_Y_Smooth = mean(Fish1_Y_Smooth),
                                                    Fish1_Z_Smooth = mean(Fish1_Z_Smooth))

nnd_joined <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y)) %>%
                                    group_by(Fish1,Frame_Num) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance <= 2 | all_nas) %>%
                                    mutate(row_n = row_number(),
                                           remove = ifelse(row_n > 1 & is.na(Distance),"Y","N")) %>%
                                    filter(remove == "N") %>%
                                    ungroup() %>%
                                    filter(Frame_Num %in% c(nnd_frame)) %>% 
                                    mutate(Grouping = paste(Frame_Num, Fish1, Fish2)) %>% 
                                    select(c(Frame_Num, Fish1, Fish2, Grouping)) %>%
                                    pivot_longer(c(Fish1, Fish2),
                                                  names_to = "Useless",
                                                  values_to = "Fish1") %>%
                                    select(-c(Useless)) %>% 
                                    left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth))

raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num/60, y = Fish1_Distance_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  geom_line(data = nnd_summary, aes(x = Frame_Num/60, y = meanNND_Smooth), color = "black", size = 1.5)+
  scale_color_manual(values = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC"))+
  theme_classic()+ 
  theme(legend.position = "none")+
  xlab("Time (s)")+
  ylab("NND (BL)")+
  ylim(0,3)

raw_nnd_plot

axis_remove <- list(showaxeslabels  = FALSE,
                    showgrid = FALSE,
                    showline = FALSE,
                    showticklabels = FALSE,
                    showspikes = FALSE,
                    showticklabels  = FALSE,
                    visible = FALSE,
                    zeroline = FALSE)

fig <- plot_ly() %>%
        #groups and colors
        # 1, 2, 3: ea4747, df1574, fdbe6f
        # 5, 8: 32CD32, 006400
        # 4, 6, 7: 4790ea, 8115df, 45dfef
        # Old: c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")
        # New: c("#ea4747","#df1574","#fdbe6f","#4790ea","#32CD32", "#8115df", "#45dfef", "#006400")

       add_trace(x = smooth_data$Fish1_X_Smooth, y = smooth_data$Fish1_Y_Smooth, z = smooth_data$Fish1_Z_Smooth,
               split = smooth_data$Fish1, type = 'scatter3d', mode = 'lines', opacity = 1, line = list(width = 6),
               color = smooth_data$Fish1,
               colors = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%

       add_trace(x = select_frames_labeled$Fish1_X_Smooth, y = select_frames_labeled$Fish1_Y_Smooth, z = select_frames_labeled$Fish1_Z_Smooth,
                 split = select_frames_labeled$Fish1, type = 'scatter3d', mode = "markers",
                 color = select_frames_labeled$Fish1,
                 colors =c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%

       add_trace(x = nnd_joined$Fish1_X_Smooth, y = nnd_joined$Fish1_Y_Smooth, z = nnd_joined$Fish1_Z_Smooth, 
                 split = nnd_joined$Grouping, type = 'scatter3d', mode = "lines", color = I("black"), line = list(shape = "spline", width = 10)) %>%

       layout(showlegend = FALSE, scene = list(aspectratio=list(x=2,y=1,z=1),
              xaxis = axis_remove, 
              yaxis = axis_remove,
              zaxis = axis_remove))

### Old Stuff
